<<<<<<< HEAD
---
title: "CASE STUDY 2"
output: html_document
---
Part 2: Cleaning the raw data
2a) Read the csv into R and take a look at the data set.  Output how many rows and columns the data.frame is.
```{r echo=TRUE}
Data <- read.csv('CaseStudy2-data.csv')

# how many rows and columns the data.frame is?
Dim=dim(Data)
cat('Number of rows are equal to',Dim[1])
cat('\nNumber of columns are equal to',Dim[2])

```
2b)The column names are either too much or not enough.  Change the column names so that they do not have spaces, underscores, slashes, and the like. All column names should be under 12 characters. Make sure you're updating your codebook with information on the tidied data set as well.
```{r, echo=TRUE}
# Here, columns have been changed manually becuase there is no unique algorithm to explain them all
names(Data)<-c("Age","Attrition","BusinessTrvl","DailyRate","Department","DistFromHome","Education","EduField","EmployeeCnt","EmployeeNum","EnvSatfction","Gender","HourlyRate","JobInvolmnt","JobLevel","JobRole","JobSatfction","MaritalStat","MonthlyIncm","MonthlyRate","NumCmpWorked","Over18","OverTime","PrcntSalHike","PerfRating","RlnSatfctn","StandardHrs","StockOptLvl","TotWrkngYrs","TrngTmsLstYr","WrkLifeBal","YrsAtCompany","YrsInCrntRl","YrsSncLstPrm","YrsWthCurMgr")

colnames(Data)
```
2c)Some columns are, due to Qualtrics, malfunctioning.
Here we chose Over18 and TrainingTimesLastYear becuase it seems unrelevent to the performance.

```{r, echo=TRUE}
Data <- subset(Data, select = -c(Over18,TrngTmsLstYr))
print(Data)
```

2d)Make sure your columns are the proper data types (i.e., numeric, character, etc.).  If they are incorrect, convert them. 
```{r, echo=TRUE}
# here we have checked all columns and correct them accordingly. Columns are either integer or factor but we have change them all to their correct format.
Data$Age <- as.integer(Data$Age)
Data$Attrition <- as.factor(Data$Attrition)
Data$BusinessTrvl <- as.factor(Data$BusinessTrvl)
Data$DailyRate <- as.integer(Data$DailyRate)
Data$Department <- as.factor(Data$Department)
Data$DistFromHome <- as.integer(Data$DistFromHome)
Data$Education <- as.integer(Data$Education)
Data$EduField <- as.factor(Data$EduField)
Data$EmployeeCnt <- as.integer(Data$EmployeeCnt)
Data$EmployeeNum <- as.integer(Data$EmployeeNum)
Data$EnvSatfction <- as.integer(Data$EnvSatfction)
Data$Gender <- as.factor(Data$Gender)
Data$HourlyRate <- as.integer(Data$HourlyRate)
Data$JobInvolmnt <- as.integer(Data$JobInvolmnt)
Data$JobLevel <- as.integer(Data$JobLevel)
Data$JobRole <- as.factor(Data$JobRole)
Data$JobSatfction <- as.integer(Data$JobSatfction)
Data$MaritalStat <- as.factor(Data$MaritalStat)
Data$MonthlyIncm <- as.integer(Data$MonthlyIncm)
Data$MonthlyRate <- as.integer(Data$MonthlyRate)
Data$NumCmpWorked <- as.integer(Data$NumCmpWorked)
Data$OverTime <- as.factor(Data$OverTime)
Data$PrcntSalHike <- as.integer(Data$PrcntSalHike)
Data$PerfRating <- as.integer(Data$PerfRating)
Data$RlnSatfctn <- as.integer(Data$RlnSatfctn)
Data$StandardHrs <- as.integer(Data$StandardHrs)
Data$StockOptLvl <- as.integer(Data$StockOptLvl)
Data$TotWrkngYrs <- as.integer(Data$TotWrkngYrs)
Data$WrkLifeBal <- as.integer(Data$WrkLifeBal)
Data$YrsAtCompany <- as.integer(Data$YrsAtCompany)
Data$YrsInCrntRl <- as.integer(Data$YrsInCrntRl)
Data$YrsSncLstPrm <- as.integer(Data$YrsSncLstPrm)
Data$YrsWthCurMgr <- as.integer(Data$YrsWthCurMgr)

Data
```




4.	Deeper Analysis and Visualization 

4a)	You should make all of these appealing looking.  Remember to include things like a clean, informative title, axis labels that are in plain English, and readable axis values that do not overlap.

4b)	Create bar charts in ggplot or similar. The bars should be in descending order, Use any color palette of your choice other than the default.
```{r, echo=True}
library(plyr)
library(ggplot2)
Dep = count(Data$Department)
Dep<- Dep[order(Dep$freq),]
Dep$x <- factor(Dep$x, levels = Dep$x[order(-Dep$freq)])
ggplot(data=Dep, aes(x=x, y=freq, fill='red'))+geom_bar(stat='identity')+xlab('Departments')+ylab('Frequency')
```

4c)	Is there a relationship between Age and Income?  Create a scatterplot and make an assessment of whether there is a relationship.  Color each point based on the Gender of the participant.  You’re welcome to use lm() or similar functions to back up your claims

```{r, echo=TRUE}
library(ggplot2)
Age <- Data$Age
Income <- Data$MonthlyIncm
Gender <- Data$Gender
ggplot(Data, aes (Income, Age, color = Gender)) + geom_point()+ggtitle("Correlation between income and age")+geom_smooth(method = lm)
cor.test(Age,Income)
```


4d)	What about Life Satisfaction?  Create another scatterplot.  Is there a discernible relationship there to what?   

```{r,echo=TRUE}

cor.test(Data$EnvSatfction,Data$Age)
cor.test(Data$EnvSatfction,Data$DailyRate)
cor.test(Data$EnvSatfction,Data$DistFromHome)
cor.test(Data$EnvSatfction,Data$Education)
cor.test(Data$EnvSatfction,Data$EmployeeCnt)
cor.test(Data$EnvSatfction,Data$EmployeeNum)
cor.test(Data$EnvSatfction,Data$JobSatfction)
cor.test(Data$EnvSatfction,Data$HourlyRate)
cor.test(Data$EnvSatfction,Data$JobInvolmnt)
cor.test(Data$EnvSatfction,Data$JobLevel)
cor.test(Data$EnvSatfction,Data$MonthlyIncm)
cor.test(Data$EnvSatfction,Data$MonthlyRate)
cor.test(Data$EnvSatfction,Data$NumCmpWorked)
cor.test(Data$EnvSatfction,Data$PrcntSalHike)
cor.test(Data$EnvSatfction,Data$PerfRating)
cor.test(Data$EnvSatfction,Data$RlnSatfctn)
cor.test(Data$EnvSatfction,Data$StandardHrs)
cor.test(Data$EnvSatfction,Data$StockOptLvl)
cor.test(Data$EnvSatfction,Data$TotWrkngYrs)
cor.test(Data$EnvSatfction,Data$WrkLifeBal)
cor.test(Data$EnvSatfction,Data$YrsAtCompany)
cor.test(Data$EnvSatfction,Data$YrsInCrntRl)
cor.test(Data$EnvSatfction,Data$YrsSncLstPrm)
cor.test(Data$EnvSatfction,Data$EnvSatfction)

ggplot(Data, aes (Data$EnvSatfction, Data$HourlyRate)) + geom_point()+ggtitle("Correlation between Environment satisfaction and Hourly Rate")+geom_smooth(method = lm)+xlab('Envoronment satisfaction')+ylab('Hourly Rate')




```




=======
---
title: "CASE STUDY 2"
output: html_document
---
Part 2: Cleaning the raw data
2a) Read the csv into R and take a look at the data set.  Output how many rows and columns the data.frame is.
```{r echo=TRUE}
Data <- read.csv('CaseStudy2-data.csv')

# how many rows and columns the data.frame is?
Dim=dim(Data)
cat('Number of rows are equal to',Dim[1])
cat('\nNumber of columns are equal to',Dim[2])

```
2b)The column names are either too much or not enough.  Change the column names so that they do not have spaces, underscores, slashes, and the like. All column names should be under 12 characters. Make sure you're updating your codebook with information on the tidied data set as well.
```{r, echo=TRUE}
# Here, columns have been changed manually becuase there is no unique algorithm to explain them all
names(Data)<-c("Age","Attrition","BusinessTrvl","DailyRate","Department","DistFromHome","Education","EduField","EmployeeCnt","EmployeeNum","EnvSatfction","Gender","HourlyRate","JobInvolmnt","JobLevel","JobRole","JobSatfction","MaritalStat","MonthlyIncm","MonthlyRate","NumCmpWorked","Over18","OverTime","PrcntSalHike","PerfRating","RlnSatfctn","StandardHrs","StockOptLvl","TotWrkngYrs","TrngTmsLstYr","WrkLifeBal","YrsAtCompany","YrsInCrntRl","YrsSncLstPrm","YrsWthCurMgr")

colnames(Data)
```
2c)Some columns are, due to Qualtrics, malfunctioning.
Here we chose Over18 and TrainingTimesLastYear becuase it seems unrelevent to the performance.

```{r, echo=TRUE}
Data <- subset(Data, select = -c(Over18,TrngTmsLstYr))
print(Data)
```

2d)Make sure your columns are the proper data types (i.e., numeric, character, etc.).  If they are incorrect, convert them. 
```{r, echo=TRUE}
# here we have checked all columns and correct them accordingly. Columns are either integer or factor but we have change them all to their correct format.
Data$Age <- as.integer(Data$Age)
Data$Attrition <- as.factor(Data$Attrition)
Data$BusinessTrvl <- as.factor(Data$BusinessTrvl)
Data$DailyRate <- as.integer(Data$DailyRate)
Data$Department <- as.factor(Data$Department)
Data$DistFromHome <- as.integer(Data$DistFromHome)
Data$Education <- as.integer(Data$Education)
Data$EduField <- as.factor(Data$EduField)
Data$EmployeeCnt <- as.integer(Data$EmployeeCnt)
Data$EmployeeNum <- as.integer(Data$EmployeeNum)
Data$EnvSatfction <- as.integer(Data$EnvSatfction)
Data$Gender <- as.factor(Data$Gender)
Data$HourlyRate <- as.integer(Data$HourlyRate)
Data$JobInvolmnt <- as.integer(Data$JobInvolmnt)
Data$JobLevel <- as.integer(Data$JobLevel)
Data$JobRole <- as.factor(Data$JobRole)
Data$JobSatfction <- as.integer(Data$JobSatfction)
Data$MaritalStat <- as.factor(Data$MaritalStat)
Data$MonthlyIncm <- as.integer(Data$MonthlyIncm)
Data$MonthlyRate <- as.integer(Data$MonthlyRate)
Data$NumCmpWorked <- as.integer(Data$NumCmpWorked)
Data$OverTime <- as.factor(Data$OverTime)
Data$PrcntSalHike <- as.integer(Data$PrcntSalHike)
Data$PerfRating <- as.integer(Data$PerfRating)
Data$RlnSatfctn <- as.integer(Data$RlnSatfctn)
Data$StandardHrs <- as.integer(Data$StandardHrs)
Data$StockOptLvl <- as.integer(Data$StockOptLvl)
Data$TotWrkngYrs <- as.integer(Data$TotWrkngYrs)
Data$WrkLifeBal <- as.integer(Data$WrkLifeBal)
Data$YrsAtCompany <- as.integer(Data$YrsAtCompany)
Data$YrsInCrntRl <- as.integer(Data$YrsInCrntRl)
Data$YrsSncLstPrm <- as.integer(Data$YrsSncLstPrm)
Data$YrsWthCurMgr <- as.integer(Data$YrsWthCurMgr)

Data
```




4.	Deeper Analysis and Visualization 

4a)	You should make all of these appealing looking.  Remember to include things like a clean, informative title, axis labels that are in plain English, and readable axis values that do not overlap.

4b)	Create bar charts in ggplot or similar. The bars should be in descending order, Use any color palette of your choice other than the default.
```{r, echo=True}
library(plyr)
library(ggplot2)
Dep = count(Data$Department)
Dep<- Dep[order(Dep$freq),]
Dep$x <- factor(Dep$x, levels = Dep$x[order(Dep$freq)])
ggplot(data=Dep, aes(x=x, y=freq, fill='red'))+geom_bar(stat='identity')
```

4c)	Is there a relationship between Age and Income?  Create a scatterplot and make an assessment of whether there is a relationship.  Color each point based on the Gender of the participant.  You’re welcome to use lm() or similar functions to back up your claims

```{r, echo=TRUE}
library(ggplot2)
Age <- Data$Age
Income <- Data$MonthlyIncm
Gender <- Data$Gender
ggplot(Data, aes (Income, Age, color = Gender)) + geom_point()+ggtitle("Correlation between income and age")+geom_smooth(method = lm)
cor.test(Age,Income)
```


4d)	What about Life Satisfaction?  Create another scatterplot.  Is there a discernible relationship there to what?   

```{r,echo=TRUE}
ggplot(Data, aes (Data$JobSatfction, Data$Age, color = Gender)) + geom_point()+ggtitle("Correlation between Job satisfaction and age")+geom_smooth(method = lm)
cor.test(Data$JobSatfction,Data$Age)
cor.test(Data$JobSatfction,Data$DailyRate)
cor.test(Data$JobSatfction,Data$DistFromHome)
cor.test(Data$JobSatfction,Data$Education)
cor.test(Data$JobSatfction,Data$EmployeeCnt)
cor.test(Data$JobSatfction,Data$EmployeeNum)
cor.test(Data$JobSatfction,Data$EnvSatfction)
cor.test(Data$JobSatfction,Data$HourlyRate)
cor.test(Data$JobSatfction,Data$JobInvolmnt)
cor.test(Data$JobSatfction,Data$JobLevel)
cor.test(Data$JobSatfction,Data$MonthlyIncm)
cor.test(Data$JobSatfction,Data$MonthlyRate)
cor.test(Data$JobSatfction,Data$NumCmpWorked)
cor.test(Data$JobSatfction,Data$PrcntSalHike)
cor.test(Data$JobSatfction,Data$PerfRating)
cor.test(Data$JobSatfction,Data$RlnSatfctn)
cor.test(Data$JobSatfction,Data$StandardHrs)
cor.test(Data$JobSatfction,Data$StockOptLvl)
cor.test(Data$JobSatfction,Data$TotWrkngYrs)
cor.test(Data$JobSatfction,Data$WrkLifeBal)
cor.test(Data$JobSatfction,Data$YrsAtCompany)
cor.test(Data$JobSatfction,Data$YrsInCrntRl)
cor.test(Data$JobSatfction,Data$YrsSncLstPrm)
cor.test(Data$JobSatfction,Data$JobSatfction)

```




>>>>>>> 6a1658ffc3dd7fba4586589c32d0b9af1b851f56
